From Reversible Programs to \\ Univalent Universes and Back

### 2021-09-05 Pi+/paper/equivalence.tex
Fix part of the typos
Consists of

\noindent Normalisation consists of translating $\PiLang$ programs to $\PiHatLang$, computing a permutation, and quoting
back to $\PiPlusLang$. Note that the normalisation happens in the step from $\PiHatLang$ to $\UFin$ and back to
$\PiHatLang$ and that normalisation also provides a decision procedure for program equivalence. Synthesis consists of
quoting permutations. More general, user-guided, reasoning can be done using the sound and complete level-2
combinators to rewrite $\PiLang$ programs.

Recall the specification of reversible disjunction from \Cref{sec:examples}, the two Qiskit circuits for implementing it, and the
corresponding $\PiLang$ definitions \Afun{reversibleOr1} and \Afun{reversibleOr2}. The normal forms for both circuit is
computes to the following, establishing their equivalence:

>>>>

\noindent Normalisation involves translating $\PiLang$ programs to $\PiHatLang$, computing a permutation, and quoting
back to $\PiPlusLang$. Note that the normalisation happens in the step from $\PiHatLang$ to $\UFin$ and back to
$\PiHatLang$ and that normalisation also provides a decision procedure for program equivalence. Synthesis happens by
quoting permutations. More general, user-guided, reasoning can be done using the sound and complete level-2
combinators to rewrite $\PiLang$ programs.

Recall the specification of reversible disjunction from \Cref{sec:examples}, the two Qiskit circuits for implementing
it, and the corresponding $\PiLang$ definitions \Afun{reversibleOr1} and \Afun{reversibleOr2}. The normal forms for both
circuit compute to the following, establishing their equivalence:
